Deciding Bitvector Termination with Program Synthesis

### 2014-07-06 papers/termination/paper.tex
related work

Somehow expected, most of the techniques are specialised in the synthesis of linear ranking functions for linear programs over integers (or rationals) \cite{DBLP:conf/pldi/CookPR06,DBLP:conf/cav/LeeWY12,DBLP:conf/popl/Ben-AmramG13,DBLP:conf/vmcai/P04,DBLP:conf/atva/HeizmannHLP13,DBLP:conf/cav/BradleyMS05,DBLP:conf/tacas/CookSZ13}. 
Among them, 
Lee et al. make use of transition predicate abstraction, algorithmic learning, and decision procedures to compute transition
invariants as proofs for the termination of linear programs \cite{DBLP:conf/cav/LeeWY12}.
Leike and Heizmann present a new method for the constraint-based synthesis
of termination arguments for linear loop programs based on
linear ranking templates \cite{DBLP:conf/tacas/LeikeH14}.
Linear ranking functions supported by inductive linear invariants for loops with linear guards and transitions: \cite{DBLP:conf/cav/BradleyMS05}. 
Learning: \cite{DBLP:conf/cav/HeizmannHP14}

>>>>

Somehow expected, most of the techniques are specialised in the synthesis of linear ranking functions for linear programs 
over integers (or rationals) \cite{DBLP:conf/pldi/CookPR06,DBLP:conf/cav/LeeWY12,DBLP:conf/popl/Ben-AmramG13,DBLP:conf/vmcai/P04,
DBLP:conf/atva/HeizmannHLP13,DBLP:conf/cav/BradleyMS05,DBLP:conf/tacas/CookSZ13}. Among them, 
Lee et al. make use of transition predicate abstraction, algorithmic learning, and decision procedures 
%to compute transition invariants as proofs for the termination of linear programs 
\cite{DBLP:conf/cav/LeeWY12},
Leike and Heizmann propose linear ranking templates 
%in order to synthesise
%termination arguments for linear loop programs 
\cite{DBLP:conf/tacas/LeikeH14}, whereas
Bradley et al. compute lexicographic linear ranking functions supported by inductive linear invariants 
%for loops with linear guards and transitions: 
\cite{DBLP:conf/cav/BradleyMS05}. 
%Learning: \cite{DBLP:conf/cav/HeizmannHP14}
